\huge Tor's Usability for Censorship Circumvention

### 2016-04-18 pets2017-paper/pets2017-paper.tex
Regen table:participant-summary.

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\
	E1-OLD & 19/19 & 100\% & 1:05 \\
	E2-NEW & 18/19 & 95\% & 3:22 \\
	E2-OLD & 16/19 & 84\% & 5:07 \\
	E3-NEW & 13/20 & 65\% & 22:19 \\
	E3-OLD & 10/20 & 50\% & 40:08 \\
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned success time for 40 minutes.}
\label{table:participant-summary}
\end{table}

\begin{figure}
\centering
\includegraphics{time_to_success_clamped}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times,
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right show the number of participants 
who did not finish in the time allotted.
Here, non-finishing participants are assigned the maximum time of 40 minutes.
}
\label{fig:time_to_success_clamped}
\end{figure}

@@

@@

\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  10\% & 24\% & 8\% & 1\% & 57\% \\
	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
	OLD & 10\% & 35\% & 11\% & 0\% & 45\% \\
	E1 & 33\% & 16\% & 23\% & 1\% & 27\% \\
	E2 & 11\% & 18\% & 8\% & 1\% & 63\% \\
	E3 & 8\% & 27\% & 8\% & 1\% & 57\% \\
	\end{tabular}
\caption{overall time} 
\label{table:overall_time}
\end{table}

\begin{table}
\centering
	\begin{tabular}{c r r r r }
	 & First & Proxy & Bridge & Summary \\
	\noalign{\hrule}
	All & 22\% & 57\% & 19\% & 2\% \\
	NEW & 40\% & 31\% & 19\% & 9\% \\ 
	OLD & 18\% & 63\% & 19\% & 0\% \\
	E1 & 45\% & 22\% & 32\% & 1\% \\
	E2 & 29\% & 48\% & 20\% & 2\% \\
	E3 & 19\% & 61\% & 18\% & 2\% \\
	\end{tabular}
\caption{active time} 
\label{table:active_time}
\end{table}

@@

% impacts of giving people advice on which transport to choose.
10 people in the new interface chose meek as their second bridge (10/15, 66\%). 
5 people in the old interface chose meek as their second bridge (5/13, 38\%).

>>>>

\begin{table}
\centering
	% Generated by info.R.
	\begin{tabular}{l r r r r}
	& \multicolumn{2}{c}{success rate} & \multicolumn{1}{c}{median time} \\
	& \multicolumn{2}{c}{after 40 minutes} & \multicolumn{1}{c}{to success} \\
	\noalign{\hrule}
	E1-NEW & 19/19 & 100\% & 0:20 \\
	E1-OLD & 19/19 & 100\% & 1:01 \\
	E2-NEW & 18/19 & 95\% & 3:32 \\
	E2-OLD & 16/19 & 84\% & 5:00 \\
	E3-NEW & 13/20 & 65\% & 20:56 \\
	E3-OLD & 10/20 & 50\% & 40:08 \\
	\end{tabular}
\caption{
A summary of participants' success in circumventing censorship
given their simulated censorship environment and version of Tor. Those who
failed to connect successfully were assigned the maximum time of 40:08.
}
\label{table:participant-summary}
\end{table}

\begin{figure}
\centering
\includegraphics{time_to_success_clamped}
\caption{
Time to first success, by censorship environment and interface.
The dots show the raw completion times,
while the boxplots show the medians and interquartile ranges.
The ``DNF'' figures at the right show the number of participants 
who did not finish in the time allotted.
Here, non-finishing participants are assigned the maximum time of 40:08
for the purpose of computing the median.
}
\label{fig:time_to_success_clamped}
\end{figure}

@@

\begin{figure} 
%\includegraphics{}
{\color {red} TODO} 
\caption{order pluggable transports were chosen}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{time_to_success_clamped}
\caption{
{\color{red} MAKE THIS FOR ACTIVE TIME}
}
\label{fig:active_time_clamped}
\end{figure}

%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
\begin{table}
\centering
	\begin{tabular}{c r r r r r}
	 & First & Proxy & Bridge & Summary & Progress \\
	\noalign{\hrule}
	All &  8\% & 18\% & 8\% & 1\% & 65\% \\
	NEW & 9\% & 7\% & 4\% & 2\% &  78\% \\
	OLD & 7\% & 25\% & 11\% & 0\% & 57\% \\
	E1 & 32\% & 16\% & 23\% & 1\% & 28\% \\
	E2 & 7\% & 10\% & 8\% & 1\% & 74\% \\
	E3 & 7\% & 21\% & 8\% & 1\% & 63\% \\
	\end{tabular}
\caption{overall time} 
\label{table:overall_time}
\end{table}

%TODO: turn it into a stacked bar chart with same colors as all-participant-edges
\begin{table}
\centering
	\begin{tabular}{c r r r r }
	 & First & Proxy & Bridge & Summary \\
	\noalign{\hrule}
	All & 23\% & 52\% & 23\% & 2\% \\
	NEW & 40\% & 31\% & 19\% & 9\% \\ 
	OLD & 17\% & 58\% & 25\% & 0\% \\
	E1 & 45\% & 22\% & 32\% & 1\% \\
	E2 & 27\% & 40\% & 29\% & 3\% \\
	E3 & 20\% & 57\% & 21\% & 2\% \\
	\end{tabular}
\caption{active time} 
\label{table:active_time}
\end{table}

@@
